**First high-frequency time series of carbonate chemistry in the Arctic**

### 2022-03-30 awipev-CO2_presentation.Rmd
New slides + updates

## **Consistency**
![ ](figures/pco2_calc_meas.png)

@@

## **Water column stratification**
::: {style="text-align:center" markdown="1"}
  ![ ](figures/deltas.png)
:::

>>>>

## **Consistency**

::: {style="text-align:center" markdown="1"}
![ ](figures/pco2_calc_meas.png)
:::

@@

## **Water column stratification**

:::: {style="display: flex;"}
::: {class='col-md-5'}

- Weird profiling
- Salinity in the bottom layer (8 to 12 m) is up to 1 unit higher than in the surface layer (0 to 4 m) in summer, 0.7 unit lower in Dec and similar in both layers at other times
- Temperature is lower by up to 2.7°C in the deep layer from Mar to Sep and higher by up to 2.4 °C in Nov-Jan
- Density is almost always higher in the bottom than in the surface layer.

:::
::: {class='col-md-5'}

  ![ ](figures/deltas.png)
:::
::::
